Can we distinguish modes of selective interactions using linkage disequilibrium?

### 2021-11-11 Manuscript.Rmd
discrete simulations

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "preamble.tex"
    citation_package: natbib
    extra_dependencies: ["float"]
bibliography: "references.bib"
biblio-style: "genetics"
title: Can we distinguish modes of selective interactions using linkage disequilibrium?
author:
header-includes:
- |
  ```{=latex}
  \usepackage{authblk}
  \author{Aaron P. Ragsdale \\ aaronpeaceragsdale@gmail.com}
  \affil{Department of Human Genetics, McGill University, Montreal, Canada \\
         National Laboratory of Genomics for Biodiversity, Irapuato, Mexico \\
         }
  ```
date: \today
---

>>>>

---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "preamble.tex"
    citation_package: natbib
    extra_dependencies: ["float"]
bibliography: "references.bib"
biblio-style: "genetics"
title: Can we distinguish modes of selective interactions using linkage disequilibrium?
author:
header-includes:
- |
  ```{=latex}
  \usepackage{authblk}
  \author{Aaron P. Ragsdale \\ aaronpeaceragsdale@gmail.com}
  \affil{Department of Human Genetics, McGill University, Montreal, Canada \\
         National Laboratory of Genomics for Biodiversity, Irapuato, Mexico \\
         }
  ```
- \usepackage{lineno}
- \linenumbers
date: \today
---
